Online {\IterComp}

### 2017-09-13 abstract.tex
And some things to fix

    Our online iterative compilation method yields programs that get 80\% of the speedup achievable by an offline oracle, 
    but without executing any input more than once, which the oracle cannot do. 
    Through probe removal we bring the instrumentation overhead down to only 4\% on average, making our
    approach suitable for regular use. We show practical online iterative compilation for the first time, 
    optimizing programs according to the range of inputs users actually present.

>>>>

    Our online iterative compilation method yields programs that get \FIXME{80\%} of the speedup achievable by an offline oracle, 
    but without executing any input more than once, which the oracle cannot do. 
    Through probe removal we bring the instrumentation overhead down to only \FIXME{4\%} on average, making our
    approach suitable for regular use. We show practical online iterative compilation for the first time, 
    optimizing programs according to the range of inputs users actually present.
